### 2015-07-01 narrative/data-desc.tex
more edits on data description.

The description of data is essentially metadata and it may include conventional attributes, such as 
data type, size, dimensionality, relationship to other data, and etc. In this project, a key metadata attribute
that enables QoS scheduling, data placement, and ???, is \textit{data utility}, which
captures the priority of objects - it is to our belief that
users must prioritize a small set of objects to be saved on 
higher-level capacity-limited storage layer in exascale
to avoid the slow access to large-capacity lower-level storage, such as tapes.
We propose a new technique, described by a utility function, where objects
can be cast into multiple buckets of data, and each bucket can be prioritized differently according
to its utility value.
Once the data is re-organized, users will be able to use API (section ??)
to describe the importance of this data.

\paragraph{State of the art:} ADIOS implements a binary-packed data format that allows
data characteristics such as min, max and index to be wrapped around data chunks. A
directy benefit is that each data chunk can be operated independently and I/O concurrenty
can be maximized. We will build upon this capability and further augment the format
to incorporate data utility.

>>>>

The description of data is essentially metadata and it may include conventional attributes, such as 
data type, size, dimensionality, relationship to other data, and etc. In particular,
relationship to other data objects can be captured by implementing \textit{soft links}
and different types of relationships can be expressed by different types of soft links. 
In this project, a key metadata attribute
that enables QoS scheduling, data placement, and ???, is \textit{data utility value}, which
captures the priority of objects - it is to our belief that
for exascale science, users must prioritize a small set of objects to be saved on 
higher-level capacity-limited storage layer
to avoid the slow access to large-capacity lower-level storage, such as tapes.
We propose a new technique, described by a utility function plugged in by a user, where objects
can be cast into multiple buckets of data, and each bucket can be prioritized differently according
to its utility value.
Once this is done, the middleware system will construct the description of data, re-organize
and place data to achieve the desired QoS goals and policies.

\paragraph{State of the art:} ADIOS implements a binary-packed data format that allows
data characteristics such as min, max and index to be wrapped around data chunks. A
direct benefit is that each data chunk can be operated independently and I/O concurrenty
can be maximized. We will build upon this capability and further augment the format
to express data utility. Recently DAMSEL \cite{damsel} provides a rich metadata representation
and management layer that captures the relationship between data blocks for scientific applications.
This allows application data to be mapped to storage system efficiently, without overburdening
users to managing complex data model, such as AMR, from the user space. However, the aspect of 
data importantance hasn't been explored, which we believe will be important for exascale storage solutions.
